draftFigure1

### 2025-12-17 dataPrep.Rmd
more surveys need to add whether barometer

@@

surveyCountries_long_clean_yearly <- surveyCountries_long_clean
surveyCountries_long_clean_yearly$year <- ifelse(surveyCountries_long_clean_yearly$year == "2017 - 2021", 2019, surveyCountries_long_clean_yearly$year)
surveyCountries_long_clean_yearly$year <- ifelse(surveyCountries_long_clean_yearly$year == "2021 - 2022", 2021, surveyCountries_long_clean_yearly$year)

@@

>>>>

surveyClassification$surveyedCountries <- ifelse(surveyClassification$surveyedCountries == "Belgium; Denmark; Germany; Spain, Greece; France; Ireland; Italy; Luxembourg; Netherlands; Portugal; United Kingdom",
                                                 "Belgium; Denmark; Germany; Spain; Greece; France; Ireland; Italy; Luxembourg; Netherlands; Portugal; United Kingdom",
                                                 surveyClassification$surveyedCountries)

@@

surveyCountries_long_clean_yearly <- surveyCountries_long_clean

table(surveyCountries_long_clean_yearly$year)

surveyCountries_long_clean_yearly$year <- ifelse(surveyCountries_long_clean_yearly$year == "2017 - 2021", 2019, surveyCountries_long_clean_yearly$year)
surveyCountries_long_clean_yearly$year <- ifelse(surveyCountries_long_clean_yearly$year == "2021 - 2022", 2021, surveyCountries_long_clean_yearly$year)

@@

```{r count eurobarometer}

library(tidyverse)
surveys <- read.csv("output/surveyClassifYear.csv")

surveys <- surveys %>% 
  filter(Inclusion == 1)

surveys <- surveys %>% 
  filter(!is.na(iso3))

surveys <- surveys %>% 
  filter(!(iso3 == "FRA" & continent == "Seven seas (open ocean)")) %>% 
  mutate(item_id = paste0(iso3, id, year)) %>%                      # unique survey item ID
  distinct(item_id, categoryPollution, category) %>%          # each item counts once per (exposure, topic)
  count(categoryPollution, category, name = "n_items") %>%    # number of items mentioning category

eurobarometer_surveys <- surveyClassification %>%
  filter(grepl("Eurobarometer", SurveyName, ignore.case = TRUE))

nrow(eurobarometer_surveys)

### 2025-12-17 draftFigure1.Rmd
fix bug year survey item
adding weighted category paper count also remove duplicate rows in dataset for FRA and CYP
more surveys need to add whether barometer

@@

my_breaks = c(1, 5, 10, 20)

@@

# 2) Build the map with integer labels and no decimals:
map_plot_clean_survey <- ggplot() +
  geom_spatvector(
    data = world_no_antarctica,
    aes(fill = n_surveys),
    color = "grey70",
    size  = 0.1
  ) +
  scale_fill_gradientn(
    colours = c("#F3EBF8", "#D4ABEF", "#541F78"),
    name    = "Papers",
    trans   = "log10",
    breaks  = my_breaks,
    labels  = label_number(
      accuracy = 1,
      big.mark = ",",
      trim     = TRUE
    ),
    na.value = "grey85"
  ) +
  coord_sf(expand = FALSE) +
  labs(
    title    = "Global Survey Question Counts by Country",
    # subtitle = "Log₁₀ scale, viridis “plasma” palette"
  ) +
  theme_void(base_size = 14) +
  theme(
    legend.position  = "bottom",
    legend.key.width = unit(2, "cm"),
    plot.title       = element_text(face = "bold", hjust = 0.5),
    plot.subtitle    = element_text(hjust = 0.5)
  )

>>>>

```{r panels with eurobarometer highlight}
library(tidyverse)
dataset <- read.csv("output/datasetPlots.csv")

@@

my_breaks = c(1, 5, 10, 30, 110)

@@

# 2) Build the map with integer labels and no decimals:
map_plot_clean_survey <- ggplot() +
  geom_spatvector(
    data = world_no_antarctica,
    aes(fill = n_surveys),
    color = "grey70",
    size  = 0.1
  ) +
  scale_fill_gradientn(
    colours = c("#F3EBF8", "#D4ABEF", "#541F78"),
    name    = "Survey items",
    trans   = "log10",
    breaks  = my_breaks,
    labels  = label_number(
      accuracy = 1,
      big.mark = ",",
      trim     = TRUE
    ),
    na.value = "grey85"
  ) +
  coord_sf(expand = FALSE) +
  labs(
    title    = "Global Survey Question Counts by Country",
    # subtitle = "Log₁₀ scale, viridis “plasma” palette"
  ) +
  theme_void(base_size = 14) +
  theme(
    legend.position  = "bottom",
    legend.key.width = unit(2, "cm"),
    plot.title       = element_text(face = "bold", hjust = 0.5),
    plot.subtitle    = element_text(hjust = 0.5)
  )
